¥documentclass[10pt]{article}

¥usepackage[margin=0.75in]{geometry}
¥usepackage{booktabs}
¥usepackage{array}
¥usepackage{tabularx}
¥usepackage{siunitx}
¥usepackage{xcolor}
¥usepackage{hyperref}

¥hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue
}

¥sisetup{
  round-mode=places,
  round-precision=2
}

¥newcommand{¥pending}{¥textcolor{gray}{pending}}

¥title{ScAN - A Path to PIM Hardware-aware Network}
¥author{}
¥date{¥today}

¥begin{document}
¥maketitle

¥section*{Student Network}

The current student network uses 4-channel RGGB input at spatial size
$16¥times16$. The first eight convolutions are
¥texttt{Conv2d + BatchNorm2d + ReLU}; the final layer is a logits convolution
followed by global average pooling.

¥begin{table}[h]
¥centering
¥small
¥begin{tabular}{@{}l l r r r r@{}}
¥toprule
Layer & Operation & $C_{¥mathrm{in}}¥rightarrow C_{¥mathrm{out}}$ & Kernel & Stride & Output ¥¥
¥midrule
1.1 & Conv+BN+ReLU & $4¥rightarrow96$ & $3¥times3$ & 1 & $96¥times16¥times16$ ¥¥
1.2 & Conv+BN+ReLU & $96¥rightarrow96$ & $3¥times3$ & 1 & $96¥times16¥times16$ ¥¥
1.3 & Conv+BN+ReLU & $96¥rightarrow96$ & $3¥times3$ & 2 & $96¥times8¥times8$ ¥¥
2.1 & Conv+BN+ReLU & $96¥rightarrow192$ & $3¥times3$ & 1 & $192¥times8¥times8$ ¥¥
2.2 & Conv+BN+ReLU & $192¥rightarrow192$ & $3¥times3$ & 1 & $192¥times8¥times8$ ¥¥
2.3 & Conv+BN+ReLU & $192¥rightarrow192$ & $3¥times3$ & 2 & $192¥times4¥times4$ ¥¥
3 & Conv+BN+ReLU & $192¥rightarrow192$ & $3¥times3$ & 1 & $192¥times4¥times4$ ¥¥
4 & Conv+BN+ReLU & $192¥rightarrow192$ & $1¥times1$ & 1 & $192¥times4¥times4$ ¥¥
5 & Conv logits + GAP & $192¥rightarrow100$ & $1¥times1$ & 1 & $100¥times4¥times4¥rightarrow100$ ¥¥
¥bottomrule
¥end{tabular}
¥end{table}

¥section*{Current Results}

¥begin{table}[h]
¥centering
¥small
¥begin{tabularx}{¥linewidth}{@{}l l l r X@{}}
¥toprule
Experiment & Precision & Eval path & Acc. (¥%) & Notes ¥¥
¥midrule
RGB FP32 reference & FP32 & float & ¥pending & Legacy RGB result should be rerun if needed for a strict comparison. ¥¥
RAW/RGGB FP32 & FP32 & float & 61.31 & Default noisy test sanity check; training-log best is 61.44. ¥¥
RAW/RGGB FP32 & FP32 & float & 61.18 & Clean test, ¥texttt{raw¥_noise=False}. ¥¥
RAW/RGGB QAT & W4A4 uniform & INT simulator & 56.61 & Current validated noisy simulator baseline. ¥¥
RAW/RGGB QAT & W4A4 uniform & INT simulator & 57.09 & Clean simulator reference from previous run. ¥¥
QKD uniform, first pass & W4A4 uniform & INT simulator & 56.02 & Worse than QAT; not accepted as final QKD. ¥¥
QKD uniform, matched schedule & W4A4 uniform & INT simulator & 56.93 & Partial CS rerun best; below non-uniform path. ¥¥
QKD non-uniform SS & W4A4 integer LUT-Q, $m=7$ & codebook INT simulator & 56.78 & Integer LUT values $[-7,¥ldots,7]$. ¥¥
QKD non-uniform SS & W4A4 integer LUT-Q, $m=15$ & codebook INT simulator & 56.52 & Integer LUT values $[-14,-12,¥ldots,14]$; training-log best 57.06. ¥¥
QKD non-uniform SS + PACT & I16/W4/A4 integer LUT-Q, $m=15$ & codebook INT simulator & 60.21 & Full rerun; training-log best 60.66. ¥¥
QKD non-uniform CS + PACT & I16/W4/A4 integer LUT-Q, $m=15$ & codebook INT simulator & 61.24 & Full rerun; training-log best 61.39. ¥¥
QKD non-uniform TU + PACT & I16/W4/A4 integer LUT-Q, $m=15$ & codebook INT simulator & ¥textbf{61.66} & Full rerun; training-log best 61.81. ¥¥
¥bottomrule
¥end{tabularx}
¥end{table}

¥section*{QKD Setup}

The teacher checkpoint ¥texttt{b4¥_100.pth} uses 4-channel RAW/RGGB input, not
RGB input. Teacher preprocessing upsamples RGGB tensors to $224¥times224$ and
normalizes with $(x-0.5)/0.5$.

¥begin{table}[h]
¥centering
¥small
¥begin{tabular}{@{}l r l@{}}
¥toprule
Teacher / stage & Acc. (¥%) & Notes ¥¥
¥midrule
EfficientNetV2-L teacher, clean & 77.30 & Verified on current H5 test split. ¥¥
EfficientNetV2-L teacher, noisy & 77.33 & Default noisy evaluation. ¥¥
Co-studied teacher, noisy & 78.70 & Earlier short CS run improved teacher. ¥¥
QKD SS rerun & 60.21 & I16/W4/A4 LUT-Q + PACT, fixed simulator. ¥¥
QKD CS rerun & 61.24 & I16/W4/A4 LUT-Q + PACT, fixed simulator. ¥¥
QKD TU rerun & 61.66 & Current best dense int4 simulator result. ¥¥
¥bottomrule
¥end{tabular}
¥end{table}

¥section*{Integer Simulator}

The dense int4 simulator is the reporting path for quantized inference. It
runs on CPU because PyTorch does not provide the exact CUDA int4/int32
convolution kernel we need here.

¥begin{itemize}
  ¥item The first layer input uses unsigned 16-bit input codes in $[0,65535]$.
  ¥item Hidden activations use unsigned 4-bit activation codes in $[0,15]$.
  ¥item Uniform weights use signed 4-bit codes in $[-7,7]$ plus per-output-channel scales.
  ¥item Non-uniform weights use 4-bit indices into an integer LUT-Q codebook; the current best checkpoint uses integer LUT values $[-14,-12,¥ldots,14]$.
  ¥item Convolution uses int32 accumulation.
  ¥item Requantization uses precomputed layer constants derived from activation and weight scales.
  ¥item BatchNorm is folded into convolution weights/bias before simulator execution.
  ¥item Weight-side QAT transforms are exported offline into integer weight codes and scales. Simulator forward does not run ¥texttt{tanh}, k-means, nearest-LUT search, or weight quantization.
  ¥item Final logits are dequantized to FP32 after the final integer convolution and then globally averaged.
¥end{itemize}

For the current uniform QAT checkpoint and non-uniform QKD checkpoints,
fake-quant and simulator reporting are aligned under deterministic loader
settings:

¥begin{table}[h]
¥centering
¥small
¥begin{tabular}{@{}l r r@{}}
¥toprule
Setting & Fake QAT (¥%) & INT simulator (¥%) ¥¥
¥midrule
Noisy, ¥texttt{raw¥_noise=True}, ¥texttt{num¥_workers=0} & 56.61 & 56.61 ¥¥
Clean, ¥texttt{raw¥_noise=False}, ¥texttt{num¥_workers=0} & 57.09 & 57.09 ¥¥
Non-uniform SS, integer LUT-Q $m=7$, noisy & 56.78 & 56.78 ¥¥
Non-uniform SS, integer LUT-Q $m=15$, noisy & 56.52 & 56.52 ¥¥
Non-uniform SS + PACT, integer LUT-Q $m=15$, I16 input, noisy & -- & 60.21 ¥¥
Non-uniform CS + PACT, integer LUT-Q $m=15$, I16 input, noisy & -- & 61.24 ¥¥
Non-uniform TU + PACT, integer LUT-Q $m=15$, I16 input, noisy & -- & 61.66 ¥¥
¥bottomrule
¥end{tabular}
¥end{table}

¥section*{PIM Conv Status}

Implemented an explicit PIM-QAT model path and PIM simulator path without
changing the default dense-QKD path. The current minimal PIM path keeps the
existing BN student model; GBN/PCN are not enabled in this pass.

The PIM path follows ¥texttt{pim¥_info/scanpcn¥_inference¥_spec.tex}: row
select over $[18,18,36,72]$ chunks, keep 48 of 144 rows by default, hybrid
stage1.1 keep 72 of 144 rows, 7-bit mid-rise tile ADC, digital BN scale/bias,
normalized hidden DAC activations in $[0,1]$, and unmasked stage1.0 / logits
layers. PIM-QAT eval and PIM simulator are numerically matched on the TU
checkpoint smoke input (¥texttt{max¥_abs¥_diff} $¥le 6¥times10^{-7}$).

¥section*{Current Best}

¥texttt{checkpoints/rerun/qkd¥_i16¥_intlut¥_pact¥_g8m15¥_lutq¥_tu.pth}

¥section*{Next Updates}

¥begin{enumerate}
  ¥item Train the PIM-QAT model from the current dense int4 checkpoint.
  ¥item Report all new PIM results through ¥texttt{pim¥_sim¥_test} with ¥texttt{raw¥_noise=True}.
  ¥item Add GBN/PCN only after the minimal BN PIM path is stable.
¥end{enumerate}

¥end{document}
